---
title: "Chapter 2"
author: "Verena und Maximilian Held"
date: "1/6/2019"
---

1. Suppose the globe tossing data had turned out to be 8 water in 15 tosses.
Construct the posterior distribution, using grid approximation.
Use the same flat prior as before.

```{r build-grid-approximation}
options(scipen=999)

# define grid
grid_res <- 200
p_grid <- seq(from = 0, to = 1, length.out = grid_res)

# define prior
prior <- rep(x = 1, times = grid_res)
prior <- prior/sum(prior)

# compute likelihood
likelihood <- dbinom(x = 8, size = 15, prob = p_grid)

# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior, so it sums to 1
posterior <- unstd.posterior / sum(unstd.posterior)

plot( p_grid , posterior , type="b" ,
    xlab="probability of water" , ylab="posterior probability" )
mtext(paste(grid_res, "points"))

```


2. Start over in 1, but now use a prior that is zero below p = 0.5 and a constant above p = 0.5.
This corresponds to prior information that a majority of the Earth’s surface is water.
What difference does the better prior make?
If it helps, compare posterior distributions (using both priors) to the true value p = 0.7.

```{r}
# define prior
prior <- ifelse(test = p_grid < 0.5, yes = 0, no = 1)
prior <- prior/sum(prior)
plot(p_grid, prior)

# compute likelihood
likelihood <- dbinom(x = 8, size = 15, prob = p_grid)
plot(p_grid, likelihood)
# compute product of likelihood and prior
unstd.posterior <- likelihood * prior

# standardize the posterior, so it sums to 1
posterior <- unstd.posterior / sum(unstd.posterior)

plot( p_grid , posterior , type="b" ,
    xlab="probability of water" , ylab="posterior probability" )
mtext(paste(grid_res, "points"))

```


3. Suppose you want to estimate the Earth’s proportion of water very precisely.
Specifically, you want the 99% percentile interval of the posterior distribution of p to be only 0.05 wide.
This means the distance between the upper and lower bound of the interval should be 0.05.
How many times will you have to toss the globe to do this?

```{r}

```

